An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2023-06-15 poly-embed-journal/poly-embed-journal.tex
Pass on H consistec paragraph

Beyond applying our fromework, we see several interesting directions for theoretical research.
Below we outline several such directions.

@@

Beyond studying convex elicitation complexity directly~\citep{ramaswamy2016convex,finocchiaro2021unifying,frongillo2021elicitation},
one promising approach to this question is to first understand the minimum $d$ for which a polyhedral surrogate $L:\reals^d\to \reals^\Y_+$ embeds $\ell$, called the \emph{embedding dimension} of $\ell$, and then relate this dimension to polyhedral, or general convex, elicitation complexity.
One reason this approach may be fruitful is that embeddings have much more structure than general convex losses, such as the fact that calibrated links arise automatically (\S~\ref{thm:thickened-separated}).
Yet from \S~\ref{sec:poly-ie-consistency} and similar observations, it may well be that the lowest possible prediction dimension is achieved by an embedding.

@@

\paragraph{Connections to $\H$-consistency and calibration}
\reviewertwo{A}
Throughout, we rely heavily on the fact that, when the hypothesis class $\H$ in question is the set of all measurable functions, then calibration is equivalent to consistency.
% However, consistency is defined by considering the optimal hypothesis over the set of all measurable functions (see \S~\ref{app:consistency}).
Calibration is no longer equivalent to consistency, however, when the hypothesis class $\H$ is restricted.
Consistency in this case is called \emph{$\H$-consistency}.
Calibration can fail to be sufficent for $\H$-consistency even in the realizable setting~\citep{long2013consistency,kuznetov2014multiclass,zhang2020bayes}.
One interesting direction is to understand if (some restricted version of) ``$\H$-embeddings'' via a polyhedral surrogate implies (1) $\H$-calibration, and (2) $\H$-consistency, which are not equivalent \citep{awasthi2021calibration,awasthi2021finer}.
\citet{awasthi2022hconsistency,awasthi2022multi} study $\H$ consistency bounds for adversarial classification and multi-class classification, though it is unclear how such bounds generalize to general finite prediction tasks.

>>>>

Beyond applying our framework, we see several interesting directions for theoretical research.
Below we outline several such directions.

@@

Beyond studying convex elicitation complexity directly~\citep{ramaswamy2016convex,finocchiaro2021unifying,frongillo2021elicitation},
one promising approach to this question is to first understand the minimum $d$ for which a polyhedral surrogate $L:\reals^d\to \reals^\Y_+$ embeds $\ell$, called the \emph{embedding dimension} of $\ell$, and then relate this dimension to polyhedral, or general convex, elicitation complexity.
One reason this approach may be fruitful is that embeddings have much more structure than general convex losses, such as the fact that calibrated links arise automatically (Theorem~\ref{thm:thickened-separated}).
Yet from \S~\ref{sec:poly-ie-consistency} and similar observations, it may well be that the lowest possible prediction dimension is achieved by an embedding.

@@

\paragraph{Connections to $\H$-consistency and calibration}
\reviewertwo{A}
Throughout, we rely heavily on the fact that, when the hypothesis class $\H$ in question is the set of all measurable functions, then calibration is equivalent to consistency.
% However, consistency is defined by considering the optimal hypothesis over the set of all measurable functions (see \S~\ref{app:consistency}).
Calibration is no longer equivalent to consistency, however, when the hypothesis class $\H$ is restricted.
Consistency in this case is called \emph{$\H$-consistency}.
Calibration can fail to be sufficent for $\H$-consistency even in the realizable setting~\citep{long2013consistency,kuznetov2014multiclass,zhang2020bayes}.
In work on $\H$-consistency, realizability assumptions often imply assumptions on the conditional distribution that exclude many of the regions causing inconsistency issues in \S~\ref{sec:applications}. \jessiet{Raf, I know you said something about the conditional distribution being a point mass, but I'm not sure I fully understand/buy the argument.}
Under these assumptions (or others), it would be interesting to understand if polyhedral embedding still implies $\H$-consistency.
Since $\H$-consistency is not equivalent to the corresponding analogue of calibration (c.f., \citep{awasthi2021calibration,awasthi2021finer}) it is unclear if our results can be immediately extended.
\citet{awasthi2022hconsistency,awasthi2022multi} additionally study surrogate regret bounds for $\H$-consistent surrogates for adversarial classification and multi-class classification, though it is unclear how such bounds generalize to general finite prediction tasks.

### 2023-06-15 poly-embed-journal/reviews/jmlr-response.tex
Pass on H consistec paragraph

    We added footnote 7 to the ``Polyhedral vs.\ smooth'' paragraph in the discussion to make the reviewer's excellent point. 
    See margin note R2: B.
    In general, we lack frameworks which can combine optimization tradeoffs with statistical tradeoffs, making it hard to say whether and when smooth vs polyhedral losses will lead to better computational or statistical performance.
    These questions appear challenging and heavily dependent on the setting (e.g.\ how costly data acquisition vs computation is).

@@

  \item \emph{Theorem 33 shows that every possible calibrated link must be produced from construction 2. I am wondering if a similar result holds for construction 1 and embedding?}

>>>>

    We added footnote 7\jessiet{double check footnote number} to the ``Polyhedral vs.\ smooth'' paragraph in the discussion to make the reviewer's excellent point. 
    See margin note R2: B.
    In general, we lack frameworks which can combine optimization tradeoffs with statistical tradeoffs, making it hard to say whether and when smooth vs polyhedral losses will lead to better computational or statistical performance.
    These questions appear challenging and heavily dependent on the setting (e.g.\ how costly data acquisition vs computation is).

@@

  \item \emph{Theorem \ref{thm:link-char} shows that every possible calibrated link must be produced from construction 2. I am wondering if a similar result holds for construction 1 and embedding?}
